---
title: "Share Phase"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(janitor)
library(skimr)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(here)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(lubridate)
```



Communicate data findings from the Analyze phase through data visualizations.  Each data visualization is part of a larger data story about the initial questions for the case study.

The Analysis phase discovered two groups of fitness users in which to target for outreach activities or further analysis. The first group are individuals who had activity of one or less hours for at least one day.  The second group of fitness members were those who had one or more days of high sedentary hours.

The data visualizations for both groups of fitness app users will be shared with stakeholders and recommendations will be made for each group in the Act phase.


```{r include=FALSE}
activity.df <- read_csv(here("analysis data", "Low_Activity_Hours.csv"))
```

```{r include=FALSE}
activity.df$DAY_NAME <- wday(activity.df$ACTIVITY_DATE, label=TRUE)
```

```{r include=FALSE}
head(activity.df)
```


```{r include=FALSE}
sedentary.df <- read_csv(here("analysis data", "High_Sedentary_Hours.csv"))
```

```{r include=FALSE}
sedentary.df$DAY_NAME <- wday(sedentary.df$ACTIVITY_DATE, label=TRUE)
```


### Low Activity Days

```{r echo=FALSE}
ggplot(activity.df, aes(DAY_NAME)) +
  geom_bar(fill="lightblue") +
  ggtitle("Low Activity Fitness Members") +
  labs(x="Day Name", y="Count of Individuals")
```


In the low activity group, Thursday has the highest number of members with zero or one hour of activity.


### High Sedentary Days

```{r echo=FALSE}
ggplot(sedentary.df, aes(DAY_NAME)) +
  geom_bar(fill="lightgreen") +
  ggtitle("High Sedentary Members") +
  labs(x="Day Name", y="Count of Individuals")
```


Tuesday's and Wednesday's have the highest number of individuals logging high sedentary hours.



```{r include=FALSE}
activity_sed.df <- read_csv(here("analysis data", "Low_Activity_and_High_Sedentary.csv"))
```


```{r include=FALSE}
activity_sed.df$DAY_NAME <- wday(activity_sed.df$ACTIVITY_DATE, label=TRUE)
```


### Analyze sleep activity

```{r include=FALSE}
sleep_activity.df <- read_csv(here("analysis data", "Sleep_Hours.csv"))
```


```{r include=FALSE}
sleep_activity.df$DAY_NAME <- wday(sleep_activity.df$SLEEP_DAY, label=TRUE)
```


```{r include=FALSE}
avg_sleep_activity <- sleep_activity.df %>% 
  group_by(DAY_NAME) %>% 
  summarize(avg_sleep_hrs = mean(sleep_hours))
```

```{r echo=FALSE}
ggplot(avg_sleep_activity, aes(x=DAY_NAME, y=avg_sleep_hrs)) +
  ggtitle("Average Sleep Hours - All Fitness Users") +
  geom_bar(stat = 'identity', fill="purple") +
  labs(x="Day", y="Average Sleep Hours")
```


For all fitness members, the average sleep hours per day is six hours or higher.  All members on average sleep more hours on Sundays and Wednesdays.


```{r include=FALSE}
avg_sleep_by_id <- sleep_activity.df %>% 
  group_by(ID, DAY_NAME) %>% 
  summarize(avg_sleep_hrs = mean(sleep_hours))
```

```{r include=FALSE}
distinct_ids <- activity_sed.df %>% 
  distinct(ID) 
```


```{r include=FALSE}
new_sleep.df <- sleep_activity.df %>% 
                filter(ID %in% distinct_ids$ID)
```

```{r include=FALSE}
avg_new_sleep.df <- new_sleep.df %>% 
  group_by(DAY_NAME) %>% 
  summarize(avg_sleep_hrs = mean(sleep_hours))
```

```{r echo=FALSE}
ggplot(avg_new_sleep.df, aes(x=DAY_NAME, y=avg_sleep_hrs)) +
  ggtitle("Individuals - Low activity and High sedentary hours") +
  geom_bar(stat = "identity", fill = "blue") +
  labs(x="Day", y="Average Sleep Hours")
```

This chart shows that the group of 24 individuals who logged both low activity and high sedentary hours sleep on average at least six hours per day.  This is equivalent to the average sleep hours for the entire group of fitness users.


### Individuals with Low Activity and High Sedentary Hours

```{r echo=FALSE, message=FALSE}
kable(distinct_ids)
```


